\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-02 analysis/RD design analysis.Rmd
modified:   analysis/RD design analysis.Rmd 	deleted:    analysis/RD_Plot_1st_Order.pdf 	deleted:    analysis/RD_Plot_2nd_Order.pdf 	deleted:    analysis/RD_Plot_3rd_Order.pdf 	modified:   analysis/final_analysis.do 	modified:   analysis/individual.do 	modified:   figures/RD_Plot_1st_Order.pdf 	modified:   figures/RD_Plot_2nd_Order.pdf 	modified:   figures/RD_Plot_3rd_Order.pdf 	new file:   figures/did_1.pdf 	deleted:    figures/did_1.tif 	new file:   figures/did_2.pdf 	deleted:    figures/did_2.tif 	new file:   figures/did_3.pdf 	deleted:    figures/did_3.tif 	new file:   figures/did_4.pdf 	d

```{r}
# these are the packages that we need to import
library(haven)
library(rdd)
library(ggplot2)
library(dplyr)
library(rdrobust)
library(plm)
library(xtable)
library(pander) # this is for table showing
library(latex2exp) # this is to export it
setwd("E:/umich/RealEstateBrokerage-main")
# need to place data on the base directory
data <- read_dta("template.dta")
working_directory <-"E:/umich/RealEstateBrokerage"
```

@@

```{r}
h = 0.066
cutoff = 0.41
running_var = panel_data$nearest_store_distances

filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]

# Export the first RD plot to its own PDF file
pdf("RD_Plot_1st_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 1,
       title = "RD-plot 1st order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community")
dev.off() # Close the PDF device

# Export the second RD plot to its own PDF file
pdf("RD_Plot_2nd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 2,
       title = "RD-plot 2nd order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community")
dev.off() # Close the PDF device

# Export the third RD plot to its own PDF file
pdf("RD_Plot_3rd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot 3rd order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community")
dev.off() # Close the PDF device
```

>>>>

```{r}
# these are the packages that we need to import
library(dplyr)
library(haven)
library(rdd)
library(ggplot2)
library(dplyr)
library(rdrobust)
library(plm)
library(xtable)
library(pander) # this is for table showing
library(latex2exp) # this is to export it
setwd("E:/umich/RealEstateBrokerage-main")
# need to place data on the base directory
data <- read_dta("template.dta")
working_directory <-"E:/umich/RealEstateBrokerage"
```

@@

```{r}
ci_level = 95
h = 0.066
cutoff = 0.41
running_var = panel_data$nearest_store_distances
running_var <- as.numeric(running_var)
filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]

# Export the first RD plot to its own PDF file
pdf("RD_Plot_1st_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 1,
       title = "RD-plot 1st order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community", col.dots = "blue")
dev.off() # Close the PDF device

# Export the second RD plot to its own PDF file
pdf("RD_Plot_2nd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 2,
       title = "RD-plot 1st order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community", col.dots = "blue")
dev.off() # Close the PDF device

# Export the third RD plot to its own PDF file
pdf("RD_Plot_3rd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot 3rd order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community", col.dots = "blue")
dev.off() # Close the PDF device
```

### 2024-07-02 manuscript/main.tex
modified:   analysis/RD design analysis.Rmd 	deleted:    analysis/RD_Plot_1st_Order.pdf 	deleted:    analysis/RD_Plot_2nd_Order.pdf 	deleted:    analysis/RD_Plot_3rd_Order.pdf 	modified:   analysis/final_analysis.do 	modified:   analysis/individual.do 	modified:   figures/RD_Plot_1st_Order.pdf 	modified:   figures/RD_Plot_2nd_Order.pdf 	modified:   figures/RD_Plot_3rd_Order.pdf 	new file:   figures/did_1.pdf 	deleted:    figures/did_1.tif 	new file:   figures/did_2.pdf 	deleted:    figures/did_2.tif 	new file:   figures/did_3.pdf 	deleted:    figures/did_3.tif 	new file:   figures/did_4.pdf 	d

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Entry Effect}
      \label{tab:entry_effect_robustness}
      \input{../result_tables/entry_effect_hetero.tex}

@@

\begin{figure}[ht]
    \centering
    \subfloat[Effect to income]{\includegraphics[width=0.5\textwidth]{../figures/did_1.pdf}\label{fig:did_income}}
    \subfloat[Effect to number of house tours]{\includegraphics[width=0.5\textwidth]{../figures/did_2.pdf}\label{fig:did_lead_times}}
    \hfill % Adds horizontal space between figures
    \subfloat[Effect to transaction period]{\includegraphics[width=0.5\textwidth]{../figures/did_3.pdf}\label{fig:negotiation_period}}
    \subfloat[Effect to price concession]{\includegraphics[width=0.5\textwidth]{../figures/did_4.pdf}\label{fig:did_price_concession}}
    \caption{Estimation of ACN Platformization Effect}
    \label{fig:dynamic_effect}
\end{figure}

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Online Consolidation Effect}
      \label{tab:heter_platform_did}
      \input{../result_tables/heter_platform_did.tex}

@@

We decided to use the so called Change-in-Change (CIC) estimator proposed by \citep{https://doi.org/10.1111/j.1468-0262.2006.00668.x}. The CIC model does not assume that the

@@

@@

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
    \caption{Robustness Check By Market Maturity Index}
    \label{tab:platform_consolidation_hetero_mature}
    \input{../result_tables/robust_mature.tex}

>>>>

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Entry Effect}
      \label{tab:entry_effect_robustness}
      \input{../result_tables/entry_effect_hetero_1.tex}

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Entry Effect (Continued)}
      \label{tab:entry_effect_robustness}
      \input{../result_tables/entry_effect_hetero_2.tex}

@@

\begin{figure}[ht]
    \centering
    \subfloat[Effect to income]{\includegraphics[width=0.5\textwidth]{../figures/did_1.pdf}\label{fig:did_income}}
    \subfloat[Effect to number of house tours]{\includegraphics[width=0.5\textwidth]{../figures/did_2.pdf}\label{fig:did_lead_times}}
    \hfill % Adds horizontal space between figures
    \subfloat[Effect to transaction period]{\includegraphics[width=0.5\textwidth]{../figures/did_3.pdf}\label{fig:negotiation_period}}
    \subfloat[Effect to price concession]{\includegraphics[width=0.5\textwidth]{../figures/did_4.pdf}\label{fig:did_price_concession}}
    \caption{Estimation of Platform Consolidation Effect}
    \label{fig:dynamic_effect}
\end{figure}

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Online Consolidation Effect}
      \label{tab:heter_platform_did}
      \input{../result_tables/heter_platform_did_1.tex}

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Online Consolidation Effect (Continued)}
      \label{tab:heter_platform_did}
      \input{../result_tables/heter_platform_did_2.tex}

@@

We decided to use the so called quantile estimator proposed by \citep{https://doi.org/10.1111/j.1468-0262.2006.00668.x}. The CIC model does not assume that the

@@

  \bibitem[Machado and Santos Silva(2019)]{machado_quantiles_2019}
Machado, J. A. F., and J. M. C. Santos Silva. 2019. Quantiles via Moments. \textit{Journal of Econometrics}, 213(1), 145-173.

@@

% \begin{table}[H]
%   \begin{center}
%     \begin{scriptsize}
%     \caption{Robustness Check By Market Maturity Index}
%     \label{tab:platform_consolidation_hetero_mature}
%     \input{../result_tables/robust_mature.tex}

%     \end{scriptsize}
%   \end{center}
% \end{table}
